---
title: "Where's the Beef?"
output: html_notebook
---

# Preliminary Research:

Big players in the beef industry : 
- 60 major beef packers in the U.S.
- 35 milliion cattle slaughtered each year = 26 billion pounds of beef
- 4 firms control about 75% of the market
  - Tyson Foods (25%)
  - Cargill Meat Solutions Corp. (21%)
  - JBS USA (18.5%)
  - National Beef Packing Co., LLC (10.5%)

```{r}
pkgs <-c('twitteR','ROAuth','httr', 'tidyverse')
for(p in pkgs) if(p %in% rownames(installed.packages()) == FALSE) {install.packages(p)}
for(p in pkgs) suppressPackageStartupMessages(library(p, quietly=TRUE, character.only=TRUE))
```

Set API Keys
```{r message=FALSE}
api_key <- "ah6EZ3hEc0wowBUKo8Bj8zPvF"
api_secret <- "Emc7XmzF329qzoV5AhczTEiKl32M2qbPJuapRKcCSGXx3AS2wC"
access_token <- "918552097645142016-uEsYo7FJNroYYwRTNXYBOuC3ejJM7oV"
access_token_secret <- "5I7sQ9YYprkpVFroeQy9suXFOqZsIKzSrW3zRRUdKk2S1"
setup_twitter_oauth(api_key, api_secret, access_token, access_token_secret)
```

Grab latest tweets
```{r}
tweets_tyson <- searchTwitter('@TysonFoods', n=500)
tweets_cargill <- searchTwitter('@Cargill', n=500)
tweets_jbs <- searchTwitter('@JBSCareers', n=500) # returning 0, now 1
#tweets_national <- searchTwitter('@_', n=3000) # can't find twitter account
```

Loop over tweets and extract text
```{r}
feed_tyson <- ldply(tweets_tyson, function(t) t$getText())
feed_cargill <- ldply(tweets_cargill, function(t) t$getText())
feed_jbs <- ldply(tweets_jbs, function(t) t$getText())
```


Clean Up Tweets
```{r}
tweets <- feed_tyson %>% unlist()

tweets <- tweets %>% 
  str_replace_all('[[:punct:]]', '') %>%
  str_replace_all('[[:cntrl:]]', '') %>% 
  iconv('UTF-8', 'ASCII') %>% 
  tolower() %>% 
  str_replace_all('[a-z]{15,}', '') %>% # removes strange mega-strings
  paste(collapse=" ") %>% 
  str_replace_all('\\shttp[\\S]*', '')  # work on taking out http terms

# tweets <- tweets %>% 
#   str_replace_all("[\\s]@[^\\s]*", "") # for Twitter handles
# tweets %>% str_replace_all("#\\S*", '') # removes hashtags
# str_replace_all('\\d+', '') # removes numbers
```

Create DF
```{r}
words <- tweets %>% 
  str_split('\\s+') %>% 
  unlist()

counts <- words %>% str_count()

word_df <- tibble(Word = words, Count = counts) %>% 
  distinct(Word, Count)
```

```{r}
word_df %>% arrange(desc(Count))
```


Generate Word Cloud
```{r}
library(wordcloud)
library(RColorBrewer)

pal <- brewer.pal(9, "BuGn")[-(1:4)] # colors

wordcloud(words = word_df$Word, word_df$Count, min.freq = min(word_df$Count), 
            random.order = FALSE, colors = pal)
```

