---
title: "Where's the Beef?"
output: html_notebook
---

# Preliminary Research:

Big players in the beef industry : 
- 60 major beef packers in the U.S.
- 35 milliion cattle slaughtered each year = 26 billion pounds of beef
- 4 firms control about 75% of the market
  - Tyson Foods (25%)
  - Cargill Meat Solutions Corp. (21%)
  - JBS USA (18.5%)
  - National Beef Packing Co., LLC (10.5%)

```{r}
pkgs <-c('twitteR','ROAuth','httr', 'tidyverse', 'plyr', 'stringr')
for(p in pkgs) if(p %in% rownames(installed.packages()) == FALSE) {install.packages(p)}
for(p in pkgs) suppressPackageStartupMessages(library(p, quietly=TRUE, character.only=TRUE))
```

Set API Keys
```{r message=FALSE}
api_key <- "xxxxxxxxxxxxxxxxx"
api_secret <- "xxxxxxxxxxxxxxxxx"
access_token <- "xxxxxxxxxxxxxxxxx"
access_token_secret <- "xxxxxxxxxxxxxxxxx"
setup_twitter_oauth(api_key, api_secret, access_token, access_token_secret)
```

Function For Getting Words From Twitter Feed
```{r}
feed_to_words <- function(raw_scrape, comp_words = NULL){
  
  feed <- raw_scrape %>% 
    ldply(function(t) t$getText())
  
  words <- feed %>% 
    unlist() %>% 
    str_replace_all('[[:punct:]]', '') %>%
    str_replace_all('[[:cntrl:]]', '') %>% 
    iconv('UTF-8', 'ASCII') %>% 
    tolower() %>% 
    str_replace_all('[a-z]{15,}', '') %>% # removes strange mega-strings
    paste(collapse=" ") %>% 
    str_replace_all('\\shttp[\\S]*', '') %>%  # work on taking out http terms
    str_split('\\s+') %>% 
    unlist()
  
  # tweets <- tweets %>% 
  #   str_replace_all("[\\s]@[^\\s]*", "") # for Twitter handles
  # tweets %>% str_replace_all("#\\S*", '') # removes hashtags
  # str_replace_all('\\d+', '') # removes numbers
  
  counts <- words %>% str_count()
  
  word_df <- tibble(Word = words, Count = counts) %>% 
    distinct(Word, Count)
  
  if(!is.null(comp_words)){
    comp_words <- comp_words %>% unlist()
    word_df <- word_df %>% 
      filter(Word %in% english_words) %>% 
      arrange(desc(Count))
  }
  return(word_df)
}
```

Grab latest tweets
```{r}
tweets_tyson <- searchTwitter('@TysonFoods', n=500)
tweets_cargill <- searchTwitter('@Cargill', n=500)
tweets_jbs <- searchTwitter('@JBSCareers', n=500) # returning 0, now 1
#tweets_national <- searchTwitter('@_', n=3000) # can't find twitter account
tweets_beef <- searchTwitter("#beef exclude:retweets", n=3200) # '#beef' tweets
```

Get Dictionary of Words to Reference
```{r}
english_words <- read_csv('words_alpha.txt') %>% unlist()
```

Apply Function to Company/Topic Tweets
```{r}
tyson <- tweets_tyson %>% feed_to_words(comp_words = english_words)
cargill <- tweets_cargill %>% feed_to_words(comp_words = english_words)
jbs <- tweets_jbs %>% feed_to_words(comp_words = english_words)
beef <- tweets_beef %>% feed_to_words(comp_words = english_words)
```
*"flavorful", "delicious", "mouthwatering", "irresistible", "ingredient", "tenderness" vs. "disgusting"*

Generate Word Cloud
```{r}
library(wordcloud)
library(RColorBrewer)

pal <- brewer.pal(9, "BuGn")[-(1:4)] # colors

wordcloud(words = word_df$Word, word_df$Count, min.freq = 10, 
            random.order = FALSE, colors = pal)
```

```{r}

```

